---
title: "Progress Update on Women Reserved Seats"
subtitle: "20220908 @ Lab Meeting"
author: "Yu-Hsin Ho"
output:
    xaringan::moon_reader:
        css: ["./style.css"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Household Bargaining

- How to explain the change in son preference / 3rd parity fertility?
- Having baby is a joint decision under household bargaining
- If role model effect is valid:
    - Powerful female politician is associated with higher bargaining power for wives
    - Husbands might be less susceptible

--

## Data

.leftcol[

#### 社會發展趨勢調查

*Survey on Social Development Trends*

- 1998, 2002
- Sample:
    - Age: 16-45
    - Married
]

.rightcol[

#### Variables

1. allocation of daily expenditures
2. parenting
3. saving and investments
4. allocation of houseworks

Dummy = 1 if woman is the decision maker / joint decision
]

---

.reg[
```{r}
htmltools::includeHTML("./SSDT_rf_bargaining.html")
```
]

---

## Concerns...

- Interpretation of coefficient
    - "Real" bargaining power?
    - Self-awareness?
--
- Measurement?
    - Over 80% reported "mutual decision" or "wife decision"
---

.reg.scale80[
```{r}
htmltools::includeHTML("./SSDT_logit_bargaining.html")
```
]

---

class: middle

## Labor Market Outcomes

- Female Labor Participation
- Wage

### Data

- End-of-year labor insurance record
- 1998 - 2005
- Sample:
    - Age: 20-60
    - Already have 2 children


---

.reg.scale80[
```{r}
htmltools::includeHTML("./labor_rf.html")
```
]

---

.reg.scale80[
```{r}
htmltools::includeHTML("./wage_rf.html")
```
]

---

class: middle

## Current findings

Likely mechanism:

  1. Woman under treatment has less son preference *(known by TSCS)*
  2. They gain more bargaining power in joint household decisions *(known by SSDT)*
  3. Pro-equal preference is then revealed through change of birth pattern *(known by birth registry)*
